
\begin{frame}[fragile]
  \frametitle{Sage Dev Scripts}

  Can develop normal tickets without using \cmd{git} or going to the
  \url{http://trac.sagemath.org} web page yourself:
  \begin{smallshell}
[vbraun@laptop]$ sage -dev help
usage: sage-dev [-h] subcommand ...

The developer interface for sage.

optional arguments:
  -h, --help            show this help message and exit

subcommands:
    abandon             Abandon a ticket or branch.
    checkout            Checkout another branch.
    comment             Add a comment to ``ticket`` on trac.
    commit              Create a commit from the pending
                        changes on the current branch.
    ...
  \end{smallshell}%$

\end{frame}


\begin{frame}[fragile]
  \frametitle{More on Dev Scripts}
  
  \begin{itemize}
  \item<1->
    Also available in a Sage session, for example
    \begin{shell}
      sage: dev.create_ticket?
      sage: dev.commit?
    \end{shell}
  \item<2-> Scripts will set up your name/email/ssh keys on first use.
  \item<3-> Not part of official Sage release yet, but usable.
  \item<4-> Scripts are included in the \cmd{public/sage-git/master}
    branch.
  \end{itemize}
  
\end{frame}



\begin{frame}
  \frametitle{Working on a Ticket}
  
  \begin{itemize}
  \item<1-> Optional: Create a ticket on trac:\\
    \cmd{sage -dev create-ticket}\\
    \cmd{sage -dev edit-ticket}
  \item<2-> Create a local branch to work on the ticket:\\
    \cmd{sage -dev checkout --ticket <number>}
  \item<3-> Work on the source code...
  \item<4-> Commit your changes:\\
    \cmd{sage -dev commit}
  \item<5-> Push your local branch to trac:\\
    \cmd{sage -dev push}
  \end{itemize}
\end{frame}



\begin{frame}
  \frametitle{Reviewing Tickets}
  
  \onslide<5->{
    \begin{alertblock}{Likely to erase the dev scripts right now}
      If you checkout a ticket that does not contain the dev scripts,
      then they will be gone after the checkout.
    \end{alertblock}
  }
  \begin{itemize}
  \item<1-> Checkout the ticket into a local branch:\\
    \cmd{sage -dev checkout --ticket <number>}
  \item<2-> If the ticket is good to go, set it to positive review:\\
    \cmd{sage -dev positive-review}
  \item<3-> If there is any remaining issue add a comment:\\
    \cmd{sage -dev comment}
  \item<4-> Or make edits yourself:\\
    \cmd{sage -dev commit}\\
    \cmd{sage -dev push}
  \end{itemize}
\end{frame}




%%% Local Variables:
%%% TeX-master: "talk.tex"
%%% eval: (TeX-PDF-mode 1)
%%% End:
